---
title: "Assignment_Week2"
author: "Hangsoo Jeong"
date: "9/15/2020"
output: html_document
---

For the second assignment, I’ll be using the following libraries.

```{r}
library(tidyverse)
library(ggplot2)
```

Also, the person-level dataset I created for the last assignment.

```{r}
person_data <- read_csv("people.csv")
```

## The continuous variables in the previous dataset.

There were three continuous variables in my person-level dataset in Massachusetts from the 1-year American Community Survey Sample from 2018.

1. Income (PINCP) (continuous)
2. Work hours per week (WKHP) (continuous)
3. Travel time to work (JWMNP) (continuous)

For each continuous variable, I will calculate the sample mean, the sample standard deviation, the 95-percent confidence interval for the population mean, and the interquartile range for each continuous variable. Also, I will create a histogram to illustrate the distribution of each variable.


## The Summary statistics of the income data.

First, the income. The Summary statistics of the income are as below.

```{r}
PINCP_summary <- summary(person_data$PINCP)
PINCP_summary
```

# The mean of the income data.

The mean of the income is 72961.97 dollars as below.

```{r}
PINCP_summary["Mean"]
```

# The standard deviation of the income data.

Here is the standard deviation of the income, and its value is 88111.95 dollars.

```{r}
sd(person_data$PINCP)
```

# The 95-percent confidence interval for the income data.

I created a one-sample t-test to get a 95-percent confidence interval for the population mean.

```{r}
conf_int <- t.test(person_data$PINCP)

conf_int
```
So, based on the data above, the 95-percent confidence interval for the income is from 72017.56 dollars to 73906.38 dollars.

# The interquartile range of the income data.

The interquartile range is from the first quartile to the third quartile of data.

```{r}
PINCP_summary["1st Qu."]
PINCP_summary["3rd Qu."]
```
Therefore, the interquartile range of the income is from 26700 dollars to 88400 dollars.

# The historgram of the income data.

Here are the two version of historgram I can create using hist() and geom_histogram() with ggplot().

```{r}
hist(person_data$PINCP)
```

```{r}
ggplot(person_data, aes(x = PINCP)) + geom_histogram()
```

The distribution is skewed to the right. It's shape looks closer to a negative binomial distribution than to a normal distribution. Based on the bump in the number of people who report earning around 5e+05 dollars as income, a group of outliers makes much money than other significant people.


## The Summary statistics of the Work hours per week data.

Same steps for the Work hours per week data. I will skip explaining each step, except the calculated values and the illustration of each data's histogram, as the only difference is variables.

```{r}
WKHP_summary <- summary(person_data$WKHP)
WKHP_summary
```

# The mean of the Work hours per week data.

```{r}
WKHP_summary["Mean"]
```

The mean of the work hours per week data is 38.49804 hours.

# The standard deviation of the work hours per week data.

```{r}
sd(person_data$WKHP)
```

The standard deviation of the work hours per week data is 12.76013 hours.

# The 95-percent confidence interval for the work hours per week data.

```{r}
conf_int <- t.test(person_data$WKHP)

conf_int
```

The 95-percent confidence interval for the work hours per week data is from 38.36127 hours to 38.63481 hours.

# The interquartile range of the work hours per week data.

```{r}
WKHP_summary["1st Qu."]
WKHP_summary["3rd Qu."]
```

The interquartile range of the work hours per week data is from 35 hours to 45 hours.

# The historgram of the work hours per week data.

```{r}
hist(person_data$WKHP)
```

```{r}
ggplot(person_data, aes(x = WKHP)) + geom_histogram()
```

The distribution is close to a normal distribution, having major population is near to mean. The average value is also the most common value, and values lower and higher than that are equally common.


## The Summary statistics of the travel time to work data.

Same steps for the travel time to work data. I will skip explaining each step, except the calculated values and the illustration of each data's histogram, as the only difference is variables.

```{r}
JWMNP_summary <- summary(person_data$JWMNP)
JWMNP_summary
```

# The mean of the travel time to work data.

```{r}
JWMNP_summary["Mean"]
```

The mean of the travel time to work data is 30.56508 minutes.

# The standard deviation of the travel time to work data.

```{r}
sd(person_data$JWMNP)
```

The standard deviation of the travel time to work data is 23.5714 minutes.

# The 95-percent confidence interval for the travel time to work data.

```{r}
conf_int <- t.test(person_data$JWMNP)

conf_int
```

The 95-percent confidence interval for the travel time to work data is from 30.31244 minutes to 30.81773 minutes.

# The interquartile range of the travel time to work data.

```{r}
JWMNP_summary["1st Qu."]
JWMNP_summary["3rd Qu."]
```

The interquartile range of the travel time to work data is from 15 minutes to 40 minutes.

# The historgram of the travel time to work data.

```{r}
hist(person_data$JWMNP)
```

```{r}
ggplot(person_data, aes(x = JWMNP)) + geom_histogram()
```

Just as the histogram of the income data, the distribution is skewed to the right. Its shape looks closer to a negative binomial distribution or a Poisson distribution than to a normal distribution. Based on the bump in the number of people who report traveling almost 150 minutes, many outliers travel much more than other significant people.


## The categorical variables in the previous dataset.

There were three categorical variables in my person-level dataset in Massachusetts from the 1-year American Community Survey Sample from 2018.

1. Housing tenure (TEN) (categorical)
2. Sex (SEX) (categorical)
3. Workload level (workload) (categorical)

I will calculate the 95-percent confidence interval for each category's proportion, only for the workload data. The workload data is the one I created from the first assignment, and the data on Housing tenure type and sex are either the information I am not interested in or less informative.


## The Summary statistics of the workload data.

# the possible categories of the workload data.

All the possible values of a categorical variable, Workload level, is as below.

```{r}
unique(person_data$workload)
```

# the 95-percent confidence interval for the proportion of the population in each category.

First, I can use the t.test() function to get the 95-percent confidence interval for the Light category. As shown below, it is from 0.1219537 to 0.1290555.

```{r}
t.test(person_data$workload == "Light")
```

Same functions for other categories. The 95-percent confidence intervals for the Medium and the Heavy are from 0.5809775 to 0.5915353 and from 0.2833842 to 0.2930938 each.

```{r}
t.test(person_data$workload == "Medium")
```

```{r}
t.test(person_data$workload == "Heavy")
```
