---
title: "Assignment_Week1"
author: "Hangsoo Jeong"
date: "9/9/2020"
output: html_document
---
## Loading libraries:

First, load the following libraries to run my code.

```{r}
library(tidycensus)
library(tidyverse)
```

## Finding variables:

For the person-level analysis, load the 1-year American Community Survey Sample from 2018.

```{r}
person_vars_2018 <- pums_variables %>%
  distinct(year, survey, var_code, 
           var_label, data_type, level) %>%
  filter(level == "person", year == 2018, survey == "acs1")
```


## Variables used:

I decided to explore tenure information at the person-level in Massachusetts. I chose the following variables to analyze the work-related characteristics of residents with different tenure types. However, if one works, it is assumed that he or she commutes.

1. Housing tenure (TEN) (categorical)
2. Sex (SEX) (categorical)
3. Income (PINCP) (continuous)
4. Work hours per week (WKHP) (continuous)
5. Travel time to work (JWMNP) (continuous)

```{r}
person_data <- get_pums(variables = c("TEN", 
                                      "SEX", 
                                      "PINCP", 
                                      "WKHP", 
                                      "JWMNP"),
                        state = "MA", 
                        year = 2018, 
                        survey = "acs1",
                        recode = TRUE) %>%
  filter(JWMNP > 0) %>%
  select(TEN_label, SEX_label, PINCP, WKHP, JWMNP)
```

## Calculating new variables:

After finding my variables, I wanted to classify the tenure by their workload to see if it is related to other variables, such as tenure types and commuting time. So, I created a categorical variable with three categories: "Heavy" if a person works more than 40 hours a week, "Medium" for between 40 to 20 hours, and "Light" otherwise. 


```{r}
person_data <- person_data %>%
  mutate(workload = case_when(WKHP > 40 ~ "Heavy",
                               WKHP <= 40 & WKHP > 20 ~ "Medium",
                               WKHP <= 20 ~ "Light")) %>%
  select(TEN_label, SEX_label, PINCP, WKHP, JWMNP, workload)
```


Now that I have calculated my variables, I'll display the first few rows of the data frame. 

```{r}
person_data
```


Here are the same rows but in a formatted table.

```{r}
knitr::kable(person_data[1:10,])
```

My final dataset has 33,441 rows, which mean my analysis will include 33,441 person-level microdata.

Finally, I'll save my data as a CSV file so I can use it later.

```{r}
write_csv(person_data, "people.csv")
```
